Time Series Modeling of Varying Complexity Captures Subdiffusive Solute Dynamics and Predicts Long Timescale Behavior in Nanoscale Pores.

### 2019-12-11 Ben_Manuscripts/stochastic_transport/Draft.tex
New figures and analysis to paper. Parallelization to scripts

  \begin{abstract}
  Mathematically modeling complex transport phenomena at the molecular level 
  can be a powerful tool for identifying transport mechanisms and predicting
  macroscopic properties. We use two different stochastic time series models,
  parameterized from long molecular dynamics (MD) simulation trajectories, in
  order to predict solute mean squared displacements (MSDs) and mean first 
  passage times (MFPTs) in macroscopic length pores. With our first model, 
  based on the anomalous diffusion theory, we show how solute dynamics can be
  modeled as a fractional diffusion process subordinate to a continuous time 
  random walk. From the MD simulations, we parameterize the distribution of 
  dwell times, hop lengths between dwells and correlation between hops. We 
  explore 2 variations of the anomalous diffusion model. The first variation
  applies a single set of parameters to the solute displacements and the second
  applies 2 sets of parameters based on the solute's radial distance from the closest pore center.
  Our second model, a generalization of Markov state models, treats the configurational
  state of the system as a Markov process, each of which has state dependent 
  transport behavior. For each state and transition between states, we parameterize
  the distribution and temporal correlation structure of positional fluctuations as
  a means of characterization and to allow us to predict solute MSDs.
  We show that our models reasonably reproduce MSDs calculated from molecular 
  simulations. The anomalous diffusion model shows superior predictive performance, 
  in many cases reproducing MD results well within error. Finally, we demonstrate 
  how one can use our models in order to calculate mean first passage time, and 
  therefore solute flux, of a given solute across a macroscopic-length pore. Overall,
  this works helps connect the relationship between microscopic chemically-dependent
  solute motions and macroscopic membrane performance.

%  Finally, we use the 
%  parameters of each model to identify specific differences in solute transport
%  behavior which can help suggest modifications that can be made to LLC membrane 
%  monomers in order to increase or reduce selectivity towards a specific solute
%  or class of solutes.

@@

  Mathematical descriptions of transport in complex separations membranes are 
  a powerful way to understand mechanisms and formulate membrane design principles. 
  \cite{vinh-thang_predictive_2013,geens_transport_2006,darvishmanesh_mass_2016}
  The complexity of a model generally parallels the complexity of the transport 
  mechanism at hand, as well as the transport information the model conveys.
  In dense homogeneous membranes, the solution-diffusion model can extract 
  diffusion and partition coefficients and has successfully predicted solute 
  transport rates.~\cite{wijmans_solution-diffusion_1995} Analogously, pore-flow
  models yield predictions of diffusion coefficients and solute transport rates 
  in nanoporous membranes.~\cite{paul_diffusive_1974} Modern single particle 
  tracking approaches take us beyond continuum modeling and allow us to 
  characterize complex diffusive behavior.~\cite{manzo_review_2015} At the molecular
  level, one can use molecular dynamics (MD) simulations to study both single 
  particle dynamics and bulk transport properties with atomic-level insight.~\cite{coscia_chemically_2019,maginn_best_2018}
  All of these approaches facilitate speculation on the molecular origins of separations
  by attempting to give a more intuitive understanding of how solutes move as a function
  of their environment, in turn suggesting experiments that could be performed.

  Highly selective separations membranes are desirable in numerous applications. 
  The ability to efficiently separate ions from saline water sources using membranes 
  has been actively pursued for years in an effort to create potable water for people 
  in water-scarce regions.~\cite{werber_materials_2016} Even in relatively safe
  municipal water supplies, there is a need for membranes that can specifically separate
  potentially harmful organic micropollutants such as fertilizers, pesticides, pharmaceuticals
  and personal care products.~\cite{barbosa_occurrence_2016} In the materials industry,
  there is a strong interest in creating breathable barriers to chemical warfare agents
  which selectively allow passage of water vapor.~\cite{mondloch_destruction_2015}
  The speed at which we achieve these or any other selective separation will be 
  heavily influenced by the quality of insights gained by the modeling approaches above.

  Lyotropic liquid crystals (LLCs) are a class of amphiphilic molecules that can be 
  cross-linked into mechanically strong and highly selective nanoporous membranes.~\cite{gin_polymerized_2008}
  LLC membranes have the potential to disrupt conventional membrane separation techniques by 
  being selective based not only on size and charge, but on solute chemical functionality
  as well.~\cite{dischinger_application_2017} One can tune the functionality of LLC monomers
  in order to enhance or weaken specific solute-membrane interactions.~\cite{dischinger_effect_2017}
  Two types of LLC membranes are in active development. The inverted hexagonal, 
  H\textsubscript{II}, LLC phase has densely packed, uniform-sized pores on the order of 1 nm
  in size. A perfectly synthesized H\textsubscript{II} phase has an ideal geometry for high
  throughput separations, however aligning the microscopic hexagonal mesophases on a large 
  scale has shown limited success.~\cite{feng_scalable_2014,feng_thin_2016} Bicontinuous cubic,
  Q\textsubscript{I}, phase LLCs share the uniform and nm-sized chemically complex pores of
  the H\textsubscript{II} phase but its geometry consists of a tortuous network of 3D 
  interconnected pores which do not require alignment.~\cite{carter_glycerol-based_2012} While 
  its pore structure may decrease a Q\textsubscript{I} membrane's permeability, it is considerably
  easier to synthesize.

  Molecular modeling may make it possible to efficiently create solute-specific separation
  membranes using the available chemical space of LLC monomers. To date, only a limited 
  subset of LLC monomers have been studied in membrane applications.
  \cite{carter_glycerol-based_2012,hatakeyama_nanoporous_2010,smith_ordered_1997,zhou_assembly_2003,resel_structural_2000}
  Even within this small subset, they have demonstrated selectivities that could not be
  explained beyond speculation and vague empirical correlations.~\cite{dischinger_application_2017}
  Atomistic molecular modeling can provide the resolution necessary to identify molecular 
  interactions that are key to separation mechanisms, allowing us to move beyond 
  Edisonian design approaches.

@@

  %BJC4: Added next two paragraphs to help ease more into time series modeling
  So far, our molecular models have provided valuable qualitative mechanistic insight 
  with some quantitative support which already allows us to speculate about new LLC
  monomer designs, however they would be of greater value to a wider audience if we 
  could provide quantitative predictions of macroscopic observables such as solute 
  flux. Due to the size of the system we are studying ($\sim$62,000 atoms) it is 
  prohibitively expensive and time-consuming to run simulations longer than 
  those performed for this work ($\sim$5 $\mu$s). And even with the relatively large 
  size of our system, we only simulate 24 solute trajectories per unit cell in order
  to minimize solute-solute interactions. This results in relatively high uncertainties
  in observables such as mean squared displacement (MSD), preventing reliable long
  timescale predictions. We are in need of a way of studying the collective motion
  of a much larger set of solute over much longer timescales.

  By reducing our MD simulations to observations of several key properties that 
  have the greatest influence on solute dynamics, we can construct many realizations
  of single solute trajectories useful for making long timescale predictions with 
  computational ease and lower uncertainties. Fortunately, there is an abundance of 
  information encoded in the complex solute trajectories. Into our model, we can 
  incorporate fluctuations and time-dependent correlations in solute position as well
  as the length of time solutes are trapped. We can add further detail by integrating
  our time series analysis with our knowledge of the primary trapping mechanisms as
  well as the solute's changing chemical environment within the heterogeneous membrane.

  In this work, we use the output of our MD simulations to construct two new classes of 
  mathematical models which can predict membrane performance while providing quantitative 
  mechanistic insights. The functional form of these models is driven by mechanistic 
  observations from our previous work and their inputs are parameterized using a 
  substantial amount of data generated by long ($\geq 5~\mu$s) MD simulations. The formulation
  of these models requires a dive into stochastically driven processes.

@@

  %BJC4: added mention of the anomalous subdiffusion model we chose 
  Our first modeling approach is based on the anomalous diffusion literature, 
  applying the mathematical formalism describing subdiffusive transport to observed
  solute trajectories. Specifically, we treated our system as an FBM process subordinate
  to a CTRW, or subordinated FBM (sFBM) for short. We fit sFBM
  models in two ways: 
  %MRS4: can you clarify the sentence below? Probably something like: uses a single set of parameters in the diffusion equations, etc.
  %BJC4: see if below helps.
  %First, based on a single set of parameters. 
  First, we parameterized solute motion using a single set of parameters fit
  to a hypothesized anomalous diffusion model. Second, we used a two-state approach
  by extracting two sets of model parameters calculated based on a solute's radial
  distance from the closest pore center. We observe different dynamical behavior of
  solute within the pore region versus within the monomer tails.

  Where applicable, the sFBM model is an elegant way to characterize single 
  particle trajectories and in addition to providing an easy and efficient way to 
  simulate solute trajectories, can be helpful in uncovering the underlying 
  solute-membrane interactions which result in observed transport mechanisms.
  It can help researchers formulate hypotheses to explain why a certain set of
  parameters is characteristic to a specific solute. This is largely the approach
  we used to discover the three primary trapping mechanisms in our previous work.~\cite{coscia_chemically_2019}
  Once one has knowledge of the primary mechanisms leading to anomalous diffusion
  behavior, one may gain additional insight by formulating a state-based model.

  %BJC4: Replaced below paragraph with above. 
%  While elegant, pure anomalous diffusion theory may in some cases give only a 
%  qualitative understanding of transport mechanisms. 
%  %MRS4: might need to provide a bit more explanation why it would be ony qualitative.  
%  %Relating it to molecular scale behavior and examples might help.
%  %BJC4: mention ageing
%  %BJC4: ?
%  Complex temporal relationships in 
%  between hops may have a significant effect on the average MSD. Inhomogeneity of 
%  a medium or multiple types of interactions may lead to a number of distinct 
%  diffusive regimes. In this case, a state based model may be useful.

%  \noindent We can use the observations of transport from our previous work in order to create 
%  state-based models.
%  \begin{itemize}
%  	\item We know that dynamics differ between solutes moving inside the pores and 
%  	in the tails.
%  	\item We can use the anomalous diffusion approach to model our data as a 
%  	function of radial distance from the closest pore center.
%  	\item Alternatively, we can abandon the anomalous diffusion theory and adapt the 
%  	methods of Markov state modeling.
%  \end{itemize}

@@

  Our second modeling approach applies an extended MSM framework to a relatively 
  small set of known states based on the three observed solute trapping mechanisms.  
  Standard MSMs are typically applied towards determining equilibrium populations
  of and the transitions between various state configurations.~\cite{bowman_using_2009} 
  %MRS4: this probably needs to be explained more explicitly, that the coordinates 
  %of the solute are generated according to the current state. 
  %BJC4: made more explicit.
  %We extend the framework
  %to include dynamics within states and between jumps. 
  We extend the framework to include state-dependent fluctuations and correlations in 
  solute position. 
  %MRS4: It makes sense to me what the below is, but probably isn't clear enough for others. 
  %BJC4: rephrased
%  That is we parameterize 
%  and incorporate into our model the magnitude and temporal correlation of
%  fluctuations in solute position while in each state as well as during transitions
%  to different states. 
  That is the magnitudes of a solute's fluctuations from its average trapped 
  position and the degree of correlation with its previous fluctuations is 
  defined by the parameters of its current state. To distinguish our approach from
  standard MSMs, we have named it the Markov state-dependent dynamical model (MSDDM).
  %BJC4: Added name of our modeling approach in last sentence

  %BJC4: making goals more explicit
  The success of our modeling approaches can be defined in two ways. First, if we
  can closely reproduce solute MSDs measured from MD simulations with realizations
  of our models, then it is likely that the model sufficiently captures solute 
  dynamics and can be used in a predictive capacity. Even if a model fails to 
  reproduce the MD MSDs, there is value in uncovering the cause of the deviation.
  The second measure of success is by analysis of the parameters defining each 
  model. The parameters themselves should provide clues that help explain solute 
  behavior in a coherent way. A model that successfully reproduces MD MSDs, but 
  with nonsensical parameters has severely diminished value as it could be a 
  consequence of luck.

  % BJC4: new paragraph
  The goal of this work is not to definitively determine which modeling approach
  is better but to evaluate their performance independently because they both
  have potential value dependent on one's research goals. The anomalous subdiffusion
  approach provides a systematic way to compare the dynamical behavior of different
  solutes based solely on the time series of their center of mass positions. The process
  of choosing the correct anomalous subdiffusion provides its own mechanistic insight
  since it requires a thorough analysis of solute time series behavior. One can then
  screen different solutes, compare the fit model parameters and relate them back to 
  differences in solute size and chemical composition. The MSDDM characterizes 
  explicitly defined trapping mechanisms, providing a clear picture of solute behavior
  while in each trapped state as well as the equilibrium occupation of each trapping state.
  It is possible to use the two models in tandem, the anomalous diffusion model to
  identify mechanisms, and the MSDDM to characterize mechanisms.

@@

  %BJC4: new
  We find that the sFBM anomalous diffusion model does the best job of reproducing
  simulation behavior of all solutes studied. Therefore, we use it to demonstrate 
  how one could predict solute flux through a theoretical pore of with an 
  experimentally relevant length.

@@

  We ran all MD simulations and energy minimizations using GROMACS 2018. 
  ~\cite{bekker_gromacs:_1993,berendsen_gromacs:_1995,van_der_spoel_gromacs:_2005,hess_gromacs_2008}
  We performed all post-simulation trajectory analysis using python scripts which 
  are available online at \\ \texttt{https://github.com/shirtsgroup/LLC\_Membranes}.
  The appropriate scripts to use for subsequent calculations are summarized in 
  Table~\ref{S-table:python_scripts} of the Supporting Information.

@@

  We considered each system to be equilibrated when the solute partitioning between the 
  pore and tail region reached apparent equilibrium and use only data after that point
  in our analysis of solute kinetics. We plotted the solute partition versus time in
  Figure~\ref{S-fig:equilibration} of the Supporting Information in order to justify 
  our choice of equilibration times for each solute.

@@

  % BJC3: x --> z since I'm measuring diffusion in the z direction?
  % MRS4: reasonable change.  Or explicitly state that you will refer to the pore axis as x. 
  % BJC4: I think it'll be less confusing to me writing it to change it to z.
  Solutes in this system exhibit subdiffusive behavior, a type of anomalous diffusion.
  During an anomalous diffusion process, the mean squared displacement (MSD)
  does not grow linearly with time, rather it follows a power law of the form:
  \begin{equation} 
  \langle z^2(t) \rangle = K_{\alpha_d}t^{\alpha_d}
  \label{eqn:msd_form}
  \end{equation} 
  where $\alpha_d$ is the anomalous exponent and $K_{\alpha_d}$ is the generalized 
  diffusion coefficient. We only calculate MSD with respect to the solutes' center of
  mass $z$-coordinate, which is oriented along the pore axis. A value of $\alpha_d < 1$
  indicates a subdiffusive process, while values of $\alpha_d = 1$ and $\alpha_d > 0$ 
  are characteristic of Brownian and superdiffusive motion respectively.

  %BJC3: removed ensemble MSD because it's not used
  We analyzed the time-averaged MSD of the simulated trajectories by measuring
  all possible displacements over time lag $\tau$:
  \begin{equation}
  \overline{z^2(\tau)} = \dfrac{1}{T - \tau}\int_{0}^{T - \tau} (z(t + \tau) - z(t))^2 dt
  \end{equation}
  where T is the length of the trajectory. Note that only the \textit{ensemble} MSD
  will reproduce the form of Equation~\ref{eqn:msd_form} in all cases. 
  %MRS4: probably need to explain in what way it is non-ergodic below, and if this is the scenario that people should care about.
  %BJC4: reworded, defined ergodicity (usually called 'weak' ergodicity breaking in literature) and
  % explained why it's not important for this study.
  In a pure CTRW, for example, the power law distribution of trapping times leads to
  weak ergodicity breaking. The time-averaged MSD is linear while the ensemble averaged
  MSD has the form of Equation~\ref{eqn:msd_form}.~\cite{meroz_toolbox_2015} With power
  law trapping behavior, the time between hops diverges so there is no characteristic
  measurement time scale of solute motion. In fact, as measurement time increases, the 
  MSD of a CTRW tends to decrease, a phenomenon called aging, because trajectories 
  with trapping times on the order of the measurement time get incorporated into the 
  calculation.~\cite{bel_weak_2005} We chose to analyze just the time-averaged MSD 
  because, compared to the ensemble average, it is a more statistically robust measure
  of the average distance a solute travels over time. Although theoretically possible, we do
  not use the MSD to calculate $\alpha_d$ because we can extract the same parameter 
  with higher precision using the dwell time distributions as described below.

@@

  \subsubsection*{Subordinated Fractional Brownian Motion}

  The solute motion in the system studied here may be consistent with 
  subordinated fractional Brownian motion (sFBM) where the parent process is FBM and 
  the leading process is a CTRW. We observe hopping and trapping which is consistent
  with a CTRW, along with negatively correlated hops which is consistent with FBM.

  One can characterize a CTRW process by the parameters which describe its dwell 
  time and hop length distributions. We used the \texttt{ruptures} python package in 
  order to automatically identify mean shifts in solute trajectories, indicating hops.\cite{truong_ruptures:_2018} 
  We used the corresponding hop lengths and dwell times between hops to construct 
  empirical distributions.

>>>>

  \begin{abstract}
  Mathematically modeling complex transport phenomena at the molecular level 
  can be a powerful tool for identifying transport mechanisms and predicting
  macroscopic properties. We use two different stochastic time series models,
  parameterized from long molecular dynamics (MD) simulation trajectories of
  a cross-linked H\textsubscript{II} phase lyotropic liquid crystal (LLC) 
  membrane, in order to predict solute mean squared displacements (MSDs) 
  and solute flux in macroscopic length pores. With our first model, based on 
  the anomalous diffusion theory, we show how solute dynamics can be modeled 
  as a fractional diffusion process subordinate to a continuous time random 
  walk. From the MD simulations, we parameterize the distribution of 
  dwell times, hop lengths between dwells and correlation between hops. We 
  explore 2 variations of the anomalous diffusion model. The first variation
  applies a single set of parameters to the solute displacements and the second
  applies 2 sets of parameters based on the solute's radial distance from the
  closest pore center. Our second model, a generalization of Markov state models,
  treats the configurational state of the system as a Markov process, each of
  which has state dependent transport behavior. For each state and transition
  between states, we parameterize the distribution and temporal correlation 
  structure of positional fluctuations as a means of characterization and to 
  allow us to predict solute MSDs. We show that our models reasonably reproduce
  MSDs calculated from MD simulations. The anomalous diffusion model shows 
  superior predictive performance, in many cases reproducing MD results well
  within error. Finally, we demonstrate how one can use our models in order to
  calculate flux of a given solute across a macroscopic-length pore and, based on 
  those quantities, the membrane's selectivity towards each solute. Overall, this
  work helps connect the relationship between microscopic chemically-dependent
  solute motions and macroscopic membrane performance.

@@

%  BJC4: Moved this paragraph to later
%  Mathematical descriptions of transport in complex separations membranes are 
%  a powerful way to understand mechanisms and formulate membrane design principles. 
%  \cite{vinh-thang_predictive_2013,geens_transport_2006,darvishmanesh_mass_2016}
%  The complexity of a model generally parallels the complexity of the transport 
%  mechanism at hand, as well as the transport information the model conveys.
%  In dense homogeneous membranes, the solution-diffusion model can extract 
%  diffusion and partition coefficients and has successfully predicted solute 
%  transport rates.~\cite{wijmans_solution-diffusion_1995} Analogously, pore-flow
%  models yield predictions of diffusion coefficients and solute transport rates 
%  in nanoporous membranes.~\cite{paul_diffusive_1974} Modern single particle 
%  tracking approaches take us beyond continuum modeling and allow us to 
%  characterize complex diffusive behavior.~\cite{manzo_review_2015} At the molecular
%  level, one can use molecular dynamics (MD) simulations to study both single 
%  particle dynamics and bulk transport properties with atomic-level insight.~\cite{coscia_chemically_2019,maginn_best_2018}
%  All of these approaches facilitate speculation on the molecular origins of separations
%  by attempting to give a more intuitive understanding of how solutes move as a function
%  of their environment, in turn suggesting experiments that could be performed.

  Highly selective separations membranes are desirable in numerous applications. 
  The ability to efficiently separate ions from saline water sources using membranes 
  has been actively pursued for years in an effort to create potable water for people 
  in water-scarce regions.~\cite{werber_materials_2016} Even in relatively safe
  municipal water supplies, there is a need for membranes that can specifically separate
  potentially harmful organic micropollutants such as fertilizers, pesticides, pharmaceuticals
  and personal care products.~\cite{barbosa_occurrence_2016} In the materials industry,
  %BJC4: made more general. 
  there is a strong interest in creating breathable fabrics % barriers 
  % to chemical warfare agents
  which selectively allow passage of water vapor.~\cite{mondloch_destruction_2015}
%  The pace at which we achieve these or any other selective separation goals will be 
%  heavily influenced by the quality of insights gained by the modeling approaches above.

  Lyotropic liquid crystals (LLCs) are a class of amphiphilic molecules that can be 
  cross-linked into mechanically strong and highly selective nanoporous membranes.~\cite{gin_polymerized_2008}
  They may provide a promising alternative to 
  % have the potential to disrupt
  conventional membrane separation techniques by being selective based not only on solute
  size and charge, but on solute chemical functionality as well.~\cite{dischinger_application_2017}
  One can tune the functionality of LLC monomers
  in order to enhance or weaken specific solute-membrane interactions.~\cite{dischinger_effect_2017}
  Two types of LLC membranes are in active development. The inverted hexagonal, 
  H\textsubscript{II}, LLC phase has densely packed, uniform-sized pores on the order of 1 nm
  in size. A perfectly synthesized H\textsubscript{II} phase has an ideal geometry for high
  throughput separations, however aligning the microscopic hexagonal mesophases on a large 
  scale has shown limited success.~\cite{feng_scalable_2014,feng_thin_2016} Bicontinuous cubic,
  Q\textsubscript{I}, phase LLCs share the uniform and nm-sized chemically complex pores of
  the H\textsubscript{II} phase but its geometry consists of a tortuous network of 3D 
  interconnected pores which do not require alignment.~\cite{carter_glycerol-based_2012} While 
  its pore structure may decrease a Q\textsubscript{I} membrane's permeability relative to the
  H\textsubscript{II} phase, it is considerably easier to synthesize at scale.

  Molecular modeling may make it possible to efficiently evaluate solute-specific separation
  membranes using the available chemical space of LLC monomers. To date, only a limited 
  subset of LLC monomers have been studied experimentally in membrane applications.
  \cite{carter_glycerol-based_2012,hatakeyama_nanoporous_2010,smith_ordered_1997,zhou_assembly_2003,resel_structural_2000}
  Even within this small subset, they have demonstrated selectivities that could not be
  explained beyond speculation and vague empirical correlations.~\cite{dischinger_application_2017}
  Atomistic molecular modeling can provide the resolution necessary to identify molecular 
  interactions that are key to separation mechanisms, allowing us to move beyond 
  Edisonian design approaches.

@@

  %BJC4: Added next two paragraphs to help ease more into time series modeling
  So far, our molecular models have provided valuable qualitative mechanistic insight 
  with some quantitative support which already allows us to speculate about new LLC
  monomer designs, however they would be of greater value to a wider audience if we 
  could provide quantitative predictions of macroscopic observables such as solute 
  flux and selectivity. Due to the size of the types of systems we are studying (at least 62,000 atoms)
  it is prohibitively expensive and time-consuming to run simulations longer than 
  those performed for this work ($\sim$5 $\mu$s). And even with the relatively large 
  size of our system, we only simulate 24 solute trajectories per unit cell in order
  to minimize solute-solute interactions. This results in relatively high uncertainties
  in observables such as mean squared displacement (MSD), preventing reliable long
  timescale predictions. We are in need of a way of studying the collective motion
  of a much larger set of solutes over much longer timescales.

  %BJC4: 1st paragraph moved to here
  Mathematical descriptions of transport in complex separations membranes are 
  a powerful way to understand mechanisms and formulate design principles. 
  \cite{vinh-thang_predictive_2013,geens_transport_2006,darvishmanesh_mass_2016}
  The complexity of a well-fit model generally parallels the complexity of the transport 
  mechanism at hand, as well as the transport information the model conveys.
  In dense homogeneous membranes, the solution-diffusion model can extract 
  diffusion and partition coefficients and has successfully predicted solute 
  transport rates.~\cite{wijmans_solution-diffusion_1995} Analogously, pore-flow
  models yield predictions of diffusion coefficients and solute transport rates 
  in nanoporous membranes.~\cite{paul_diffusive_1974} Modern single particle 
  tracking approaches have taken researchers beyond continuum modeling allowing them to 
  characterize complex diffusive behavior.~\cite{manzo_review_2015} At the molecular
  level, one can use molecular dynamics (MD) simulations to study both single 
  particle dynamics and bulk transport properties with atomic-level insight.~\cite{coscia_chemically_2019,maginn_best_2018}
  All of these approaches facilitate generation of hypotheses about the
  molecular origins of separations by attempting to give a more intuitive 
  understanding of how solutes move as a function of their environment, in turn
  suggesting experiments that could be performed.

  %BJC4: Tried to make this paragraph connect to previous a little better
  Using a bottom-up modeling approach, we can parameterize single particle behavior
  by reducing our MD simulations to observations of several key properties
  that have the greatest influence on solute dynamics and then construct an ensemble 
  of characteristic single solute trajectories useful for making long timescale
  predictions with computational ease and lower uncertainties. Fortunately, there 
  is an abundance of information encoded in the complex solute trajectories. Into a
  model, we can incorporate fluctuations and time-dependent correlations in solute
  position as well as the length of time solutes are trapped. We can add further
  detail by integrating our time series analysis with our knowledge of the primary
  trapping mechanisms as well as the solute's changing chemical environment within
  the heterogeneous membrane.

%  By reducing our MD simulations to observations of several key properties that 
%  have the greatest influence on solute dynamics, we can construct many realizations
%  of single solute trajectories useful for making long timescale predictions with 
%  computational ease and lower uncertainties. Fortunately, there is an abundance of 
%  information encoded in the complex solute trajectories. Into a model, we can 
%  incorporate fluctuations and time-dependent correlations in solute position as well
%  as the length of time solutes are trapped. We can add further detail by integrating
%  our time series analysis with our knowledge of the primary trapping mechanisms as
%  well as the solute's changing chemical environment within the heterogeneous membrane.

  In this work, we use the output of our MD simulations to construct two new classes of 
  mathematical models which aim to predict membrane performance while providing quantitative 
  mechanistic insights. The functional form of these models is driven by mechanistic 
  observations from our previous work and their inputs are parameterized using a 
  substantial amount of data generated by long ($\geq 5~\mu$s) MD simulations. The formulation
  of these models requires a dive into stochastically driven processes.

@@

  %BJC4: added mention of the anomalous subdiffusion model we chose 
  Our first modeling approach is based on the anomalous diffusion literature, 
  applying the mathematical formalism describing subdiffusive transport to observed
  solute trajectories. Specifically, we treated our system as an FBM process subordinate
  to a CTRW, or subordinated FBM (sFBM) for short. We fit sFBM
  models in two ways: First, we parameterized solute motion using a single set of parameters fit
  to a hypothesized anomalous diffusion model. Second, we used a two-state approach
  by extracting two sets of model parameters calculated based on a solute's radial
  distance from the closest pore center. This allows us to include different dynamical
  behavior of solutes observed within the pore region versus within the monomer tails.

  Where applicable, the sFBM model is an elegant way to characterize single 
  particle trajectories and in addition to providing an easy and efficient way to 
  simulate solute trajectories, can help uncover the underlying solute-membrane
  interactions which result in observed transport mechanisms. It can help 
  researchers formulate hypotheses to explain why a certain set of parameters is
  characteristic to a specific solute. This is largely the approach we used to
  discover the three primary trapping mechanisms in our previous work.~\cite{coscia_chemically_2019}
  Once one has knowledge of the primary mechanisms leading to anomalous diffusion
  behavior, one may gain additional insight by formulating a state-based model.

@@

  Our second modeling approach applies an extended MSM framework to a relatively 
  small set of known states based on the three previously observed solute trapping mechanisms.  
  Standard MSMs are typically applied to determine equilibrium populations
  of and the kinetics of transitions between various state configurations.~\cite{bowman_using_2009} 
  We extend the framework to include state-dependent fluctuations and correlations in 
  solute position. The magnitudes of a solute's fluctuations from its average trapped 
  position and the degree of correlation with its previous fluctuations is 
  determined by the current state. To distinguish our approach from standard MSMs, we have
  named it the Markov state-dependent dynamical model (MSDDM).

  %BJC4: making goals more explicit
  We determine the degree of success of our modeling approaches in two ways. First,
  if we can closely reproduce solute MSDs measured from MD simulations with realizations
  of our models, then it is likely that the model sufficiently captures solute 
  dynamics and can be used in a predictive capacity. Even if a model fails to 
  reproduce the MD MSDs, there is value in uncovering the cause of the deviation.
  The second measure of success is by analysis of the parameters defining each 
  model. The parameters themselves should provide clues that help explain solute 
  behavior in a coherent way. A model that successfully reproduces MD MSDs, but 
  with nonsensical parameters has severely diminished value as it could be a 
  consequence of luck.

  % BJC4: new paragraph
  The goal of this work is not to definitively determine which modeling approach
  is better but to evaluate their performance independently because they both
  have potential value dependent on one's research goals. The anomalous subdiffusion
  approach provides a systematic way to compare the dynamical behavior of different
  solutes based solely on the time series of their center of mass positions. The process
  of choosing the correct anomalous subdiffusion provides its own mechanistic insight
  since it requires a thorough analysis of solute time series behavior. One can simulate
  different solutes, compare the fit model parameters and relate them back to 
  differences in solute size and chemical composition. The MSDDM characterizes 
  explicitly defined trapping mechanisms, providing a clear picture of solute behavior
  while in each trapped state as well as the equilibrium occupation of each trapping state.
  It is possible to use the two models in tandem, the anomalous diffusion model to
  identify mechanisms, and the MSDDM to characterize mechanisms.

@@

  Finally, we use our most promising model in order to predict solute flux and 
  selectivity in pores of macroscopic length, thus achieving a better understanding
  of macroscopic properties on the basis of microscopic dynamics. We show that 
  anti-correlated solute hopping behavior severely reduces flux relative to 
  uncorrelated behavior. We use the relative solute fluxes to calculate the 
  membrane's selectivity between all pairs of solutes and demonstrate that, when 
  solutes display different degrees of anti-correlated hopping behavior, selectivity
  becomes a function of pore length. With this improved understanding of 
  macroscopic behavior, we can begin to think more critically about how to design 
  membranes in order to selectively pass or reject specific solutes.

%  We find that the sFBM anomalous diffusion model does the best job of reproducing
%  simulation behavior of all solutes studied. Therefore, we use it to demonstrate 
%  how one could predict solute flux through a theoretical pore of with an 
%  experimentally relevant length.

@@

  We ran all MD simulations and energy minimizations using GROMACS 2018.  %BJC4: version 2018. That's it not 2018.3 or anything. 
  ~\cite{bekker_gromacs:_1993,berendsen_gromacs:_1995,van_der_spoel_gromacs:_2005,hess_gromacs_2008}
  We performed all post-simulation trajectory analysis using python scripts which 
  are available online at \\ \texttt{https://github.com/shirtsgroup/LLC\_Membranes}.
  The appropriate scripts to use for subsequent calculations are summarized in 
  Table~\ref{S-table:python_scripts} of the Supporting Information.

@@

  We considered each system to be equilibrated when the solute partitioning between the 
  pore and tail region reached apparent equilibrium and use only data after that point
  in our analysis of solute kinetics. We plot the solute partition versus time in
  Figure~\ref{S-fig:equilibration} of the Supporting Information in order to justify 
  our choice of equilibration times for each solute.

@@

  Solutes in this system exhibit subdiffusive behavior, a type of anomalous diffusion.
  During an anomalous diffusion process, the mean squared displacement (MSD)
  does not grow linearly with time, but instead it follows a power law of the form:
  \begin{equation} 
  \langle z^2(t) \rangle = K_{\alpha_d}t^{\alpha_d}
  \label{eqn:msd_form}
  \end{equation} 
  where $\alpha_d$ is the anomalous exponent and $K_{\alpha_d}$ is the generalized 
  diffusion coefficient. We only calculate MSD with respect to the solutes' center of
  mass $z$-coordinate, which is oriented along the pore axis. A value of $\alpha_d < 1$
  indicates a subdiffusive process, while values of $\alpha_d = 1$ and $\alpha_d > 0$ 
  are characteristic of Brownian and superdiffusive motion respectively.

  We analyzed the time-averaged MSD of the simulated trajectories by measuring
  all possible displacements over time lag $\tau$:
  \begin{equation}
  \overline{z^2(\tau)} = \dfrac{1}{T - \tau}\int_{0}^{T - \tau} (z(t + \tau) - z(t))^2 dt
  \end{equation}
  where T is the length of the trajectory. Note that only the \textit{ensemble} MSD
  will reproduce the form of Equation~\ref{eqn:msd_form} in all cases. The ensemble
  MSD is given by:
  \begin{equation}
  \langle z^2(t) \rangle = \langle z(t) - z(0) \rangle^2
  \label{eqn:ensemble_msd}
  \end{equation} 
  In a pure CTRW, for example, the power law distribution of trapping times leads to
  weak ergodicity breaking. The time-averaged MSD is linear while the ensemble averaged
  MSD has the form of Equation~\ref{eqn:msd_form}.~\cite{meroz_toolbox_2015} With power
  law trapping behavior, the time between hops diverges so there is no characteristic
  measurement time scale of solute motion. In fact, as measurement time increases, the 
  average MSD of a CTRW tends to decrease, a phenomenon called aging, because trajectories 
  with trapping times on the order of the measurement time get incorporated into the 
  calculation.~\cite{bel_weak_2005} We chose to analyze just the time-averaged MSD 
  because, compared to the ensemble average, it is a more statistically robust measure
  of the average distance a solute travels over time. Although theoretically possible, we do
  not use the MSD to calculate $\alpha_d$ because we can extract the same parameter 
  with higher precision using the dwell time distributions as described below.

@@

  \subsubsection{Subordinated Fractional Brownian Motion}\label{method:sfbm}

%  BJC4: I say something to the following effect in the intro
%  The solute motion in the system studied here may be consistent with 
%  subordinated fractional Brownian motion (sFBM) where the parent process is FBM and 
%  the leading process is a CTRW. We observe hopping and trapping which is consistent
%  with a CTRW, along with negatively correlated hops which is consistent with FBM.

%  We modeled solute motion as a continuous time random walk (CTRW) subordinate to 
%  fractional Brownian motion, also called subordinated fractional Brownian motion (sFBM).
%  We modeled solute motion as a CTRW subordinate to FBM, also called sFBM.

  One can characterize the CTRW component of an sFBM process by the parameters which describe
  its dwell time and hop length distributions. We used the \texttt{ruptures} python
  package in order to automatically identify mean shifts in solute trajectories, 
  indicating hops.\cite{truong_ruptures:_2018} We used the corresponding hop lengths
  and dwell times between hops to construct empirical distributions.

  \textit{Dwell time distributions:} For subdiffusive transport, the distribution 
  of dwell times is expected to fit a power law distribution 
  proportional to $t^{-1-\alpha_d}$.~\cite{meroz_toolbox_2015}
  Because we are limited to taking measurements at discrete intervals dictated by the output 
  frequency of our simulation trajectories, we fit the empirical dwell times
  to a discrete power law distribution whose maximum likelihood $\alpha_d$ 
  parameter we calculated by maximizing the likelihood function: 
  \begin{equation}
	\mathcal{L}(\beta) = -n\ln \zeta(\beta, t_{min}) -
	\beta\sum_{i=1}^{n} \ln t_i 
  \label{eqn:powerlaw_likelihood}
  \end{equation}
  where $\beta = 1 + \alpha_d$, $t_i$ are collected dwell time data points,
  $n$ the total number of data points, and $\zeta$ is the Hurwitz zeta function
  where $t_{min}$ is the smallest measured value of	$t$.~\cite{clauset_power-law_2009}
